---
title: "Mini-Project 2"
author: "Your Name Here"
date: "March 24, 2017"
output: html_document
---


## Required libraries
```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

## Loading the data
```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

## Data wrangling
```{r}
library(dplyr)
```

Group by committee id and find average donation amt
```{r}
table1 <- contributions %>%
  group_by(cmte_id) %>%
  summarise(avg_contrib = mean(transaction_amt))
```

Select specific variables from committees
```{r}
table2 <- committees %>%
  select(cmte_id, cmte_name, tres_name, cmte_state, cmte_party_affiliation, connected_org_name)
```

```{r}
ourtable <- table2 %>%
  full_join(table1, by = "cmte_id")
glimpse(ourtable)
```

```{r}
newTable <- na.omit(ourtable)
glimpse(newTable)
```


```{r}
stateTable <- newTable%>%
  group_by(cmte_state)%>%
  summarise(stateAverage = mean(avg_contrib))%>%
  filter(cmte_state != "GU") %>%
  filter(cmte_state != "PR") %>%
  filter(cmte_state != "MP") %>%
  filter(cmte_state != "VI") %>%
  arrange(desc(stateAverage))
  
```

```{r}
ggplot(stateTable, aes(x = reorder(cmte_state, stateAverage), y = stateAverage)) + geom_bar(stat = "identity") + coord_flip() 
```

A pipeline to find mean contributions by party affiliation in NY
```{r}
ourtable %>%
  select(Party = cmte_party_affiliation, State = cmte_state, Donations = avg_contrib) %>%
  group_by(Party) %>%
  filter(State == "NY") %>%
  summarise(AvgDonations = mean(Donations))
```

Make that pipeline into a function to find mean contributions by party affiliation in different states
```{r}
ByState <- function(state_arg) {
  ourtable %>%
  select(Party = cmte_party_affiliation, State = cmte_state, Donations = avg_contrib) %>%
  group_by(Party) %>%
  filter(State == state_arg) %>%
  summarise(AvgDonations = mean(Donations))
}
```

Try using the function on one state
```{r}
ByState(state_arg = "NY")
```

***Need to get rid of NAs

Create a list of states, and use function ByState on each state
```{r}
state_lst <- c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY")

lapply(state_lst, FUN = ByState)
```

