---
title: "Mini-Project 2"
author: "JiYoung Yun, Emma Utz, Katherine Lemiesz"
date: "March 26, 2017"
output: html_document
---


```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggthemes)
```

```{r, include=FALSE}
load("committees.rda")
load("contributions.rda")
```

## Data wrangling
Group `contributions` data frame by committee ID and find average donation amount per committee.
```{r}
table1 <- contributions %>%
  group_by(cmte_id) %>%
  summarise(avg_contrib = mean(transaction_amt))
```

Select specific variables from the `committees` data frame for analysis.
```{r}
table2 <- committees %>%
  select(cmte_id, cmte_name, tres_name, cmte_state, cmte_party_affiliation, connected_org_name)
```

Join the restructured `table1` and `table2` by `cmte_id` (committee id).
```{r}
ourtable <- table2 %>%
  full_join(table1, by = "cmte_id")
glimpse(ourtable)
```

Get rid of rows without a specified party (NAs).
```{r}
newTable <- na.omit(ourtable)
glimpse(newTable)
```

Group the new data frame, `newTable`, by state and filter out non-states (donations were recieved from other areas, such as Puerto Rico which is designated by PR). Compute the average contribuation size per state, then arrange the table by descending contribution size.
```{r}
stateTable <- newTable%>%
  group_by(cmte_state)%>%
  summarise(stateAverage = mean(avg_contrib))%>%
  filter(cmte_state != "GU") %>%
  filter(cmte_state != "PR") %>%
  filter(cmte_state != "MP") %>%
  filter(cmte_state != "VI") %>%
  arrange(desc(stateAverage))
  
```

Make a visualization of the state averages for comparison. We chose a bar graph because each state's contribution is independent of the other states' contributions. It is also an easy way to visually compare the states.
```{r}
stateAveragePlot <-ggplot(stateTable, aes(x = reorder(cmte_state, stateAverage), y = stateAverage, fill= stateAverage)) + geom_bar(stat = "identity") + coord_flip() + scale_color_hue()+ labs(title = "Average Committee Contribution by State", x="State", y = "State Average Contribution")

stateAveragePlot
```



A pipeline funciton to find mean contributions by party affiliation
```{r}
partyContribution <-function(state_arg) {
  newTable %>%
  select(Party = cmte_party_affiliation, State = cmte_state, Donations = avg_contrib) %>%
  group_by(Party) %>%
  filter(State == state_arg) %>%
  summarise(AvgDonations = mean(Donations))
}
```

Try applying the function to various states we're interested in based off our Average State Contribution data visualization:
```{r}
state_lst <- c("NV", "CO", "FL", "NH", "NC", "OH", "VA","WI","IA","ME")
lapply(state_lst, FUN = partyContribution)
```

